Aligning species range data to better serve science and conservation

### 2016-01-14 ms_2_intro_res_disc.Rmd

For `r n_q2_am_sm` of `r n_q2` species in this quadrant (`r round((n_q2_am_sm/n_q2) * 100, 1)`%), the IUCN extent is larger than the AquaMaps extent.  By itself, this is not surprising; but for many of these species, a quick look at the maps (see SOM for examples) shows that the IUCN range hews closely to the AquaMaps range, while adding a significant buffer zone.  Coral species dominate this quadrant (`r n_q2_corals` coral species - `r round(n_q2_corals/n_corals * 100, 1)`% of all corals and `r round(n_q2_corals/n_q2 * 100, 1)`% of all species in quadrant 2).  We suspect that many of these extent-misaligned map pairs can be easily explained: most corals and reef-associated organisms prefer shallower waters; seafloor depth is explicitly modeled in AquaMaps, but not explicitly considered in IUCN range considerations. (For examples and details, see SOM)

@@

* ___Q4: more data-poor models and fewer reviewed species maps; data-rich models and expert review improve AquaMaps duh...___
* ___recommend filtering for occurcells >= 10, and where possible, giving extra weight to reviewed maps___

>>>>

For `r n_q2_am_sm` of `r n_q2` species in quadrant 2 (`r round((n_q2_am_sm/n_q2) * 100, 1)`%), the IUCN extent is larger than the AquaMaps extent.  By itself, this is not surprising; but for many of these species, a quick look at the maps (see SOM for examples) shows that the IUCN range hews closely to the AquaMaps range, while adding a significant buffer zone.  Coral species dominate this quadrant (`r n_q2_corals` coral species - `r round(n_q2_corals/n_corals * 100, 1)`% of all corals and `r round(n_q2_corals/n_q2 * 100, 1)`% of all species in quadrant 2).  We suspect that many of these extent-misaligned map pairs can be easily explained: most corals and reef-associated organisms prefer shallower waters; seafloor depth is explicitly modeled in AquaMaps, but not explicitly considered in IUCN range considerations. (For examples and details, see SOM)

@@
